### 2022-02-16 introduction/introduction.tex
more

>>>>

Earliest attempts to automate higher-order logic can be traced back to Robinson
[ehoh 23]. His approach was based on translating higher-order logic to
first-order logic using combinators, similar to the approach taken by hammers.
Huet [ehoh 16] and Andrews [ehoh 2] designed calculi that are directly applied
on higher-order formulas.

These attempts resulted in early higher-order theorem provers. Andrews and
collegaues developed TPS: a semi-automatic prover which allows user to specify
proof outlines, based on expansion proofs. Benzm\"uller and colleageues
developed LEO, a prover based on higher-order resolution which introduced
cooperative paradigm. Provers of this paradigm invoke first-order back-ends in
regular intervals to finish the proof. Latest iteration in LEO family of provers
is Leo-III.
